Viewing Computer Science through Citation Analysis

### 2019-12-20 Scientometrics/comp.tex
Scientometrics Submission

\title{Viewing Computer Science through Citation Analysis}
%\thanks{Grants or other notes
%about the article that should go on the front page should be
%placed here. General acknowledgments should be placed at the end of the article.}
\subtitle{Salton and Bergmark Redux}
%\titlerunning{Short form of title}        % if too long for running head

@@

\begin{acknowledgements}
Research and development reported in this publication was partially supported by funds from the National Institute on Drug Abuse, National Institutes of Health, US Department of Health and Human Services, under Contract No HHSN271201800040C (N44DA-18-1216). TW is supported by the Grainger Foundation.
\end{acknowledgements}

>>>>

\title{Viewing Computer Science through Citation Analysis}

\thanks{Research and development reported in this publication was partially supported by funds from the National Institute on Drug Abuse, National Institutes of Health, US Department of Health and Human Services, under Contract No HHSN271201800040C (N44DA-18-1216). TW is supported by the Grainger Foundation.}
\subtitle{Salton and Bergmark Redux}
%\titlerunning{Short form of title}        % if too long for running head

@@

\begin{acknowledgements} The authors thank Henry Small for very helpful discussions.
\end{acknowledgements}
